My title

### 2023-03-12 outputs/paper/paper.qmd
- Updated the comments on "03-rough_work" - Started adding to the "paper" Quarto doc

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

\newpage

\appendix

@@

\newpage

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
# Set up workspace

install.packages("kableExtra")
install.packages("tidyverse")

library(kableExtra)
library(tidyverse)
```

```{r}
#| include: false
# Import cleaned data from the outputs folder, originally imported via the 01-download_data.R file
cleaned_2016gss_data <- read.csv(here::here("outputs/data/cleaned_2016gss_data.csv"))
```

@@

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Weekly Total of Internet Use by Marital Status
#| echo: false
## Graph Marital Status VS. Internet Hours ##
mean_marital <- cleaned_2016gss_data %>%
  select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Marital Status`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Marital Status", values_from = c("Mean_total"))

## mutate from wide to long 
mean_marital <- melt(mean_marital)  #the function melt reshapes it from wide to long
mean_marital <- mean_marital[-6,]  # delete NA row

# save mean data
write_csv(mean_marital, "outputs/data/mean_marital.csv")

# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Internet Usage Hours"
  )
```

```{r}
## Graph Level of Happiness VS. Internet Hours##
mean_happy<- cleaned_2016gss_data %>%
  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Level of Happiness`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))

## mutate from wide to long 
mean_happy <- melt(mean_happy)  #the function melt reshapes it from wide to long
mean_happy <- mean_happy[-4,]  # delete NA row

# save mean data
write_csv(mean_happy, "outputs/data/mean_happy.csv")

# use tidyverse-style code to pivot and summarise the data 
mean_happy |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Level of Happiness",
    y = "Internet Usage Hours"
  )
```

@@

@@

@@
